ADC: Analog-to-digital converter. Convertidor analógico-digital

API: Application Programming Interface.

BBC: British Broadcasting Corporation

BLE: Bluetooth Low Energy.

BR: Bluetooth Basic Rate. 

BT: Bluetooth

CAN: Controller Area Network

CIFS: Common Internet File System

CISA: Certified Information Systems Auditor.

EDR: Bluetooth Enhanced Data Rate.

FTP: File Transfer Protocol. Protocolo de Transferencia de Archivos.

GPIO: General Purpose Input Output.

GPRS: Global System for Mobile Communications

HDMI: High-Definition Multimedia Interface. Interfaz multimedia de alta definición.

HMI: Human-Machine Interface. Interfaz Humano-Máquina

IBM: International Business Machines

IDE: Integrated Development Environment.

IEEE: Institute of Electrical and Electronics Engineering

IoT: Internet of Things.

ISM: Industrial, Scientific and Medical Radio Band.

ISS: International Space Station

JS: JavaScript

LCID: Laboratorio de Control, Investigación y Digitales

MAC: Media Access Control

NIST: National Institute of Standards and Technology. Instituto Nacional de Estándares y Tecnología.

NRCC: National Research Canada Council

OS: Operative System.

PID: Proportional Integral Derivative controller.

PUMA: Programmable Universal Machine for Assembly, o Programmable Universal Manipulation Arm.

PWM: Pulse Width Modulation.

RF: Radiofrecuencia

RTOS: Real Time Operative System. Sistema Operativo de Tiempo Real.

RX: Recepción.

SDK: Software Development Kit. Kit de Desarrollo de Software.

SFTP: SSH File Transfer Protocol. Protocolo Seguro de Transferencia de Archivos.

SIG: Special Interest Group

SMB: Server Message Block

SoC: System on Chip.

SRMS: Shuttle Remote Manipulator System

SSH: Secure Shell.

SSHFS: Secure Shell File System. 

TCP: Transmission Control Protocol. Protocolo de Control de Transmisión.

TX: Transmisión.

UART: Universal Asynchronous Receiver Transmitter.

UMTS: Universal Mobile Telecommunications System

WPA: Wi-Fi Protected Access.

WPAN: Wireless Personal Area Network.